The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method \& TESS Light Curves from XXX Clusters

### 2019-04-25 paper/ms.tex
minor paper update

Our approach follows from the algorithm presented by
\citet{Alard_Lupton_1998}, and explained in detail by
\citet{miller_optimal_2008}.
The process is: %FIXME: following miller 2008...
\begin{enumerate}
  \item Select a set of isolated stars (``stamps'').
  \item Choose basis vectors $K_n$ for the kernel, $K = \sum_{n=1}^N
    a_n K_n$. Our goal is to determine the best-fitting coefficients
    $a_n$. 
  \item Using these stamps and the least-squares method, ...
\end{enumerate}

@@

In general though, one must adapt detrending procedures to the data at
hand.  In \S~\ref{sec:flux_vs_external_parameters}, we show that the
``external parameter'' dependence visible in the TESS data is rather
complex: ordinary linear model-fitting, as well as an initial attempts
at non-linear model fitting, are poor descriptions of the data.  We go
on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
detrending approach for the purpose of transit discovery is to simply
decorrelate against other nearby stars with standard TFA.

@@

This requires selecting ``template stars'', which are a subsample of
star that are supposed to represent all the types of systematics
across the dataset. 
%FIXME: clarify this procedure
We select 500 template stars randomly from the stars on-chip with
$G_{\rm R_p}$ magnitudes between 8.5 and 13 (TODO: rather bright?).
We additionally require these stars to not have excessive variability,
by fitting a parabola in the RMS-magnitude plane, and discarding stars
more than $4\sigma$ away from the prediction of this fit.

>>>>

Our approach follows from the algorithm presented by
\citet{Alard_Lupton_1998}, and explained in detail by
\citet{miller_optimal_2008}.
The process is: %FIXME: following miller 2008...
\begin{enumerate}
  \item Select a set of isolated stars (``stamps'').
  (For ficonv, the default procedure is: grid up the image. Within
    each grid... find the brightest nonsaturated region. Use that to
    fit the kernel!)
  \item Choose basis vectors $K_n$ for the kernel, $K = \sum_{n=1}^N
    a_n K_n$. Our goal is to determine the best-fitting coefficients
    $a_n$. 
  \item Using these stamps and the least-squares method, ...
\end{enumerate}

@@

%FIXME TURGID PROSE
In general though, one must adapt detrending procedures to the data at
hand.  In \S~\ref{sec:flux_vs_external_parameters}, we show that the
``external parameter'' dependence visible in the TESS data is rather
complex: ordinary linear model-fitting, as well as an initial attempts
at non-linear model fitting, are poor descriptions of the data.  We go
on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
detrending approach for the purpose of transit discovery is to simply
decorrelate against other nearby stars with standard TFA.

@@

This requires selecting ``template stars'', which are a subsample of
star that are supposed to represent all the types of systematics
across the dataset. 
%FIXME: clarify this procedure
We select XXX template stars randomly from the stars on-chip with
$G_{\rm R_p}$ magnitudes between 8.5 and 13 (TODO: rather bright?).
As an initial variability cut, we fit a parabola in the RMS-magnitude
plane, and discarding stars more than $2\sigma$ away from the
prediction of the fit.

We then perform an initial iteration of TFA, on only the candidate
template stars.
We inspect the resulting detrended lightcurves for residual
structure by computing a Lomb-Scargle periodogram.
If the maximum-power peak has a false alarm probability below 0.1\%, 
we exclude the star from the list of candidate template stars, on the
basis of its presumed periodic variability signal.

We then randomly select 200 template stars from the remaining
non-variable candidates. 
The choice of number of template stars was discussed by (CITE KOVACS).
While it can be optimized by constructing and minimizing a BIC-like 
quantity, a little overfitting is acceptable for our puposes.
